---
title: "Assignment 4"
author: "Lukas van der Watt"
date: "10/23/2021"
output:
  word_document: default
  pdf_document: default
---

```{r} 
#Importing libraries to be able to run the lp models
library(lpSolve)
library(lpSolveAPI)
#Reading the .lp file which contains the formulation of the HeartStart problem
x <- read.lp("HeartStart.lp")
x
solve(x) #Solving the lp formulation. Since an output of [0] is produced we know it was solved successfully
get.objective(x) # Getting the value of Z (objective function)
get.variables(x) # Output of the variables indicate how many AED's should be produced for the optimal solution.
#get.constraints(x)
```
We can see that the optimal solution for the AED production & shipping is:
0  units (of xa1) in Plant A and warehouse 1
60 units (of xa2) in Plant A and warehouse 2
40 units (of xa3) in Plant A and warehouse 3 
0  units (of xa4) in Plant A and warehouse 4
80 units (of xb1) in Plant B and warehouse 1
0  units (of xb2) in Plant B and warehouse 2
30 units (of xb3) in Plant B and warehouse 3
10 units (of xb4) in Plant B and warehouse 4
These combinations will minimize the cost of production and shipping.
```{r}
#Reading the .lp file which contains the formulation of the Oil Distribution problem
y <- read.lp("OilDistribution.lp")
solve(y) #Solving the lp formulation. Since an output of [0] is produced we know it was solved successfully
get.objective(y) # Getting the value of Z (objective function)
get.variables(y)
get.constraints(y)
```
